Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2016-01-22 paper.tex
Text wrapping
Whitespace
Define abbreviations in K equation
Bring back comma

The relative importance of various physical processes on mean streamwise
momentum and kinetic energy transport/recovery in the streamwise direction were
assessed by examining the governing equations rearranged to isolate the
streamwise partial derivative ($\partial / \partial x$) for the quantities of
interest~\cite{Bachant2015-JoT}, \emph{i.e.}, momentum:

\begin{equation}
	\begin{split}
		\frac{\p U}{\p x} = 
		\frac{1}{U} \bigg{[}
		& - V\frac{\p U}{\p y}
		- W\frac{\p U}{\p z} \\
		& -\frac{1}{\rho}\frac{\p P}{\p x} \\
		& - \frac{\p}{\p x} \overline{u'u'}
		- \frac{\p}{\p y} \overline{u'v'}
		- \frac{\p}{\p z} \overline{u'w'} \\
		& + \nu\left(\frac{\p^2 U}{\p x^2}
		+ \frac{\p^2 U}{\p y^2}
		+ \frac{\p^2 U}{\p z^2} \right)
		\bigg{]},
	\end{split}
	\label{eq:momentum}
\end{equation}
and mean kinetic energy:
\begin{equation}
	\begin{split}
		\frac{\p K}{\p x}
		=
		\frac{1}{U}
		\bigg{[}
		& - \underbrace{V \frac{\p K}{\p y}}_{y\text{-adv.%please define/check the convention
		}}
		- \underbrace{W \frac{\p K}{\p z}}_{z\text{-adv.}}
		% Pressure work:
		- \frac{1}{\rho}\frac{\p}{\p x_j} P U_i \delta_{ij}
		% Work by viscous forces
		+ \frac{\p}{\p x_j} 2 \nu U_i S_{ij} % Not sure if that's capital S...
		% Turbulent transport of K
		- \underbrace{
		\frac{1}{2}\frac{\p}{\p x_j} \overline{u_i' u_j'} U_i
		}_{\text{Turb.%please define/check the convention
		trans.%please define/check the convention
		}} \\
		% Production of k
		& + 
		\underbrace{
		\overline{u_i' u_j'} \frac{\p U_i}{\p x_j}
		}_{k\text{-prod.%please define/check the convention
		}}
		% Mean dissipation
		- 
		\underbrace{
		2 \nu S_{ij}S_{ij}
		}_{\text{Mean diss.%please define/check the convention
		}}
		\bigg{]}.
	\label{eq:K-full}
	\end{split}
\end{equation}

Note that Equations~(\ref{eq:momentum}) and (\ref{eq:K-full}) only differ from the
typical forms of the mean momentum and mean kinetic energy equations by a factor
of $1/U$, but importantly, the other convective terms ( $\partial U/\partial y$,
$\partial U/\partial z$ and $\partial K/\partial y$, $\partial K/\partial z$ )
are moved to the right-hand sides of the equations to illustrate with what sign
they add to the streamwise recovery of streamwise momentum or mean kinetic
energy.

>>>>

The relative importance of various physical processes on mean streamwise
momentum and kinetic energy transport/recovery in the streamwise direction were
assessed by examining the governing equations rearranged to isolate the
streamwise partial derivative ($\partial / \partial x$) for the quantities of
interest~\cite{Bachant2015-JoT}, \emph{i.e.}, momentum:
\begin{equation}
	\begin{split}
		\frac{\p U}{\p x} = 
		\frac{1}{U} \bigg{[}
		& - V\frac{\p U}{\p y}
		- W\frac{\p U}{\p z} \\
		& -\frac{1}{\rho}\frac{\p P}{\p x} \\
		& - \frac{\p}{\p x} \overline{u'u'}
		- \frac{\p}{\p y} \overline{u'v'}
		- \frac{\p}{\p z} \overline{u'w'} \\
		& + \nu\left(\frac{\p^2 U}{\p x^2}
		+ \frac{\p^2 U}{\p y^2}
		+ \frac{\p^2 U}{\p z^2} \right)
		\bigg{]},
	\end{split}
	\label{eq:momentum}
\end{equation}
and mean kinetic energy:
\begin{equation}
	\begin{split}
		\frac{\p K}{\p x}
		=
		\frac{1}{U}
		\bigg{[}
		& - \underbrace{V \frac{\p K}{\p y}}_{y\text{-adv.%please define/check the convention
		}}
		- \underbrace{W \frac{\p K}{\p z}}_{z\text{-adv.}}
		% Pressure work:
		- \frac{1}{\rho}\frac{\p}{\p x_j} P U_i \delta_{ij}
		% Work by viscous forces
		+ \frac{\p}{\p x_j} 2 \nu U_i S_{ij} % Not sure if that's capital S...
		% Turbulent transport of K
		- \underbrace{
		\frac{1}{2}\frac{\p}{\p x_j} \overline{u_i' u_j'} U_i
		}_{\text{Turb.%please define/check the convention
		trans.%please define/check the convention
		}} \\
		% Production of k
		& + 
		\underbrace{
		\overline{u_i' u_j'} \frac{\p U_i}{\p x_j}
		}_{k\text{-prod.%please define/check the convention
		}}
		% Mean dissipation
		- 
		\underbrace{
		2 \nu S_{ij}S_{ij}
		}_{\text{Mean diss.%please define/check the convention
		}}
		\bigg{]},
	\label{eq:K-full}
	\end{split}
\end{equation}
where advection is abbreviated by ``adv.,'' turbulent transport by ``turb.
trans.,'' production by ``prod.,'' and dissipation by ``diss.''

Note that Equations~(\ref{eq:momentum}) and (\ref{eq:K-full}) only differ from
the typical forms of the mean momentum and mean kinetic energy equations by a
factor of $1/U$, but importantly, the other convective terms ( $\partial
U/\partial y$, $\partial U/\partial z$, and $\partial K/\partial y$, $\partial
K/\partial z$ ) are moved to the right-hand sides of the equations to illustrate
with what sign they add to the streamwise recovery of streamwise momentum or
mean kinetic energy.
